### 2015-04-16 README.Rmd
Added superscripts

Thomas E. White<sup>1</sup>, Rhiannon L. Dalrymple2, Daniel W. A. Noble1,2, James C. O’Hanlon 1, Daniel B. Zurek3, Kate D. L. Umbers4,5,6

1 Department of Biological Sciences, Macquarie University, North Ryde, NSW, Australia, 2109 2 Evolution & Ecology Research Centre, School of Biological, Earth and Environmental Sciences, University of New South Wales, Kensington, NSW, Australia, 2022 3 Department of Biological Sciences, University of Pittsburgh, Pittsburgh, PA, USA, 15260 4 School of Biological Sciences, University of Wollongong, Wollongong, NSW, Austrlaia 2252 5 Centre for Evolutionary Biology, University of Western Australia, Crawley, WA, Australia 6008 6 School of Science and Health, University of Western Sydney Hawkesbury, NSW, Australia 2751

>>>>

Thomas E. White<sup>1</sup>, Rhiannon L. Dalrymple<sup>2</sup>, Daniel W. A. Noble<sup>1,2</sup>, James C. O’Hanlon<sup>1</sup>, Daniel B. Zurek<sup>3</sup>, Kate D. L. Umbers<sup>4,5,6</sup>

<sup>1</sup> Department of Biological Sciences, Macquarie University, North Ryde, NSW, Australia, 2109 <sup>2</sup> Evolution & Ecology Research Centre, School of Biological, Earth and Environmental Sciences, University of New South Wales, Kensington, NSW, Australia, 2022 <sup>3</sup> Department of Biological Sciences, University of Pittsburgh, Pittsburgh, PA, USA, 15260 <sup>4</sup> School of Biological Sciences, University of Wollongong, Wollongong, NSW, Austrlaia 2252 <sup>5</sup> Centre for Evolutionary Biology, University of Western Australia, Crawley, WA, Australia 6008 <sup>6</sup> School of Science and Health, University of Western Sydney Hawkesbury, NSW, Australia 2751
